Stack Safety as a Security Property

### 2020-07-08 main.tex
CP - 6

\rb{Better section name and headings, references.}

\paragraph*{Micropolicies}
%
In order to enforce a given security policy on a system dynamically, we resort
to a programmable, tag-based reference monitor that runs alongside the program.
To control this monitor, we use a programming model that allows fine-grained
manipulation of metadata tags to encode so-called \emph{micropolicies}
\rb{cite}.

@@

Efficient execution of these micropolicies relies on hardware implementations
such as the PUMP architecture \rb{cite}, which include a monitor rule cache that
maps tag inputs to outputs and a mechanism to trap misses to software handlers
and thereby compute the transfer function of the software-defined policy.
Previous work has shown that a wide range of micropolicies can be defined and
enforced efficiently \rb{cite}.
%
\rb{Maybe go into more detail, examples later\ldots or try to segue into stack
policies}

\paragraph*{A conservative policy}
%
The first micropolicy we present to enforce the definition of stack safety
developed in \cref{sec:lse-and-wbcf} is very similar to the Depth Isolation
policy presented by \citet{DBLP:conf/sp/RoesslerD18}. Their policy tags the
stack memory with ownership information associated to each stack frame (and to
each separate object inside that frames, a more finely grained access control
that we do not need to consider here), and registers holding stack pointers with
matching access permission information. Beyond those capabilities, the compiler
generates designated sequences of instructions with special tags that grant them
permission to manage the stack, say during calls and returns. \rb{Conceivably on
alloc operations, etc., which we have not yet mentioned.}

>>>>

In this section we are going to see how an existing enforcement mechanism,
Depth Isolation from \citet{DBLP:conf/sp/RoesslerD18}, can implement
the formal stack safety property described in the previous section: it in
fact enforces a stronger, inductive version of it that strengthens the
local state encapsulation component by checking for integrity and
confidentiality violations at every step of the callee's execution trace.

\paragraph*{Micropolicies}
%
The enforcement policy of \citeauthor{DBLP:conf/sp/RoesslerD18} relies
on programmable, tag-based reference monitor that runs alongside the
program.  To control this monitor, they use a programming model that
allows fine-grained manipulation of metadata tags to encode so-called
\emph{micropolicies}~\citep{pump_oakland15}.

@@

Efficient execution of these micropolicies relies on hardware
implementations, such as the PUMP architecture~\citep{pump_oakland15},
which include a monitor rule cache that maps tag inputs to outputs and
a mechanism to trap misses to software handlers and thereby compute
the transfer function of the software-defined policy.  Previous work
has shown that a wide range of micropolicies can be defined and
enforced efficiently \rb{cite}.
%
\rb{Maybe go into more detail, examples later\ldots or try to segue into stack
policies}

\paragraph*{A conservative policy}
%
The first micropolicy we present to enforce the definition of stack
safety developed in \cref{sec:lse-and-wbcf} is \leo{a small variation
  of?}  the Depth Isolation policy presented by
\citet{DBLP:conf/sp/RoesslerD18}. Their policy tags the stack memory
with ownership information associated to each stack frame (and to each
separate object inside that frames, a more finely grained access
control that we do not need to consider here), and registers holding
stack pointers with matching access permission information. Beyond
those capabilities, the compiler generates designated sequences of
instructions with special tags that grant them permission to manage
the stack, say during calls and returns. \rb{Conceivably on alloc
  operations, etc., which we have not yet mentioned.}
